### 2021-12-08 documents/sections/extensions.tex
trimming waiwaian

\subsubsection{\PWai \rc{k-}}
\label{sec:waiwaian}
This extension, one of the Parukotoan innovations discussed in \cref{sec:extensions_intro}, created the \hixka pattern from \cref{sec:intro}.
In \PWai, the new \gl{1}\gl{s_p_} prefix \rc{k-}, innovated in \PPar, was further extended to \gl{1}\gl{s_a_}.
For regularly inflected verbs, this created a unified \gl{1}\gl{s} category \pcref{tab:pwaireg}.
\input{floats/pwaireg}

@@

There are three more verbs which did not take innovative \rc{k-} in \PWai, shown alongside \rc{ka} \qu{to say} in \cref{tab:pwaiverbs}.
The two forms for \qu{to be} are straightforwardly reconstructible, whereas \qu{to go} is somewhat of a special case.
While \hixka has the expected \obj{ɨ-}, \waiwai seems to have combined innovative \obj{k-} with the old \rc{w-}, an etymological analysis also considered by \textcite[90]{gildea1998}.
Alternatively, this form might have been influenced by deverbalized forms of \qu{to go}, where a reflex of the \gl{s_a_} class marker \rc{w-} has become fossilized \exref{waiwto}.

\pex<waiwto> \waiwai reflexes of the \gl{s_a_} class marker \rc{w-}
\a \obj{o-\emp{w}to-topo-nho} \qu{my trip} \parencite[92]{waiwaihawkins1998}
\a \obj{o-\emp{w}to-t͡ʃhe} \qu{after I went} \parencite[165]{waiwaihawkins1998}
\a \obj{kɨ-\emp{w}to-me} \qu{for us to go} \parencite[204]{waiwaihawkins1998}
\xe
%
In any case, this was a subsequent development, as the prefix pattern in \hixka \qu{to go} clearly shows that \PWai first person form \rc{wɨ-tom-} can be reconstructed.

>>>>

\subsubsection{\PWai \rc{k-}}
\label{sec:waiwaian}
This extension, one of the Parukotoan innovations discussed in \cref{sec:extensions_intro}, resulted in the \hixka patterns from \cref{sec:intro}.
In \PWai, the \gl{1}\gl{s_p_} prefix \rc{k-} innovated in \PPar was further extended to \gl{1}\gl{s_a_}.
For regularly inflected verbs, this created a unified \gl{1}\gl{s} category \pcref{tab:pwaireg}.
\input{floats/pwaireg}

@@

There are three more verbs which did not take innovative \rc{k-} in \PWai, shown alongside \rc{ka} \qu{to say} in \cref{tab:pwaiverbs}.
The two forms for \qu{to be} are straightforwardly reconstructible, whereas \qu{to go} is a special case.
While \hixka has the expected \obj{ɨ-}, \waiwai seems to have combined innovative \obj{k-} with the old \rc{w-}, an etymological analysis also considered by \textcite[90]{gildea1998}.
Alternatively, this form may have been influenced by deverbalized forms of \qu{to go}, where a reflex of the \gl{s_a_} class marker \rc{w-} has become fossilized \parentext{e.g., \obj{o-\emp{w}to-topo-nho} \qu{my trip} \parencite[92]{waiwaihawkins1998}}
%
%\pex<waiwto> \waiwai reflexes of the \gl{s_a_} class marker \rc{w-}
%\a \obj{o-\emp{w}to-topo-nho} \qu{my trip} \parencite[92]{waiwaihawkins1998}
%\a \obj{o-\emp{w}to-t͡ʃhe} \qu{after I went} \parencite[165]{waiwaihawkins1998}
%\a \obj{kɨ-\emp{w}to-me} \qu{for us to go} \parencite[204]{waiwaihawkins1998}
%\xe
%
In any case, the prefix pattern in \hixka \qu{to go} clearly shows that a \PWai first person form \rc{wɨ-tom-} can be reconstructed.
